---
title: "R Notebook"
output: html_notebook
---

Tutorial:
https://satijalab.org/seurat/cell_cycle_vignette.html


```{r}
library(Seurat)
```


```{r}
seurobj <- readRDS('data/10x-normalized-scaled-clustered-tsne.rds')
```

Inspect genes that account for the largest variation in the dataset. (Cell cycle genes MKI67 and CENPF in PC1).

```{r}
PrintPCA(seurobj, pcs.print=1:10, genes.print=5)
```

Assign cell cycle scores.
Assign each cell a score based on the expression of G2/M and S phase markers. The cell cycle marker genes are obtained from Tirosh et al, 2015. 

```{r}
cc.genes <- readLines('data/regev_lab_cell_cycle_genes.txt')
s.genes <- cc.genes[1:43]
g2m.genes <- cc.genes[44:97]
seurobj <- CellCycleScoring(seurobj, s.genes = s.genes, g2m.genes = g2m.genes, set.ident = TRUE)
head(seurobj@meta.data[22:24])
```

Visualize the distribution of some cell cycle markers. 
Most cells seem to express neither of the markers here. 

```{r}
RidgePlot(seurobj, features.plot = c("PCNA", "TOP2A", "CENPF", "MKI67"), nCol = 2)
```

Plot the first two PCs, colored on cell cycle phase.
The cell cycle effects clearly account for a large part of the variation in the dataset.

```{r}
PCAPlot(seurobj)
```

PCA only on cell cycle genes

```{r}
seurobj2 <- RunPCA(object = seurobj, pc.genes = c(s.genes, g2m.genes), do.print = FALSE)
PCAPlot(object = seurobj2)
```

In the tSNE plot, cells of the same cell cycle group together.

```{r}
TSNEPlot(seurobj, pt.size=0.1)
```


```{r}
TSNEPlot(seurobj, pt.size=0.1, group.by='sample_name', do.label = T)
```


Regress the cell cycle effects out.

```{r}
seurobj <- ScaleData(seurobj, vars.to.regress = c("nUMI", "percent.mito", "S.Score", "G2M.Score"), display.progress = T)
saveRDS(seurobj, 'data/10x-normalized-scaled-clustered-ccregout.rds')
```

Check by plotting the first two PCs again.

```{r}
RunPCA(seurobj, pcs.compute=20)
PCAPlot(seurobj)
```

And PCA only on cell cycle genes

```{r}
seurobj2 <- RunPCA(object = seurobj, pc.genes = c(s.genes, g2m.genes), do.print = FALSE)
PCAPlot(object = seurobj2)
```

Run tSNE on the new data.
Determine nr of PC's to use. 

```{r}
PCElbowPlot(seurobj)
```

Cells in different stages of the cell cycle are now more mixed. 

```{r}
seurobj <- RunTSNE(seurobj, reduction.use='pca', dims.use=1:12)
TSNEPlot(seurobj, pt.size=0.1)
```



```{r}
TSNEPlot(seurobj, group.by='sample_name', do.label=T, pt.size=0.1)
```

```{r}
TSNEPlot(seurobj, group.by='sample_name2', pt.size=0.1)
```

```{r}

```



```{r}
seurobj <- readRDS('data/10x-normalized-scaled-clustered-ccregout.rds')
```

