---
title: "R Notebook"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: 
      smooth_scroll: true
---

Analysis of the 10x samples.
- tSNE plots
- Cell cycle regression
- PCA 
- Alignment
- Marker gene expression
- tSNE colored on metadata

```{r}
library(Seurat)
library(ggplot2)
all10x <- readRDS('/projects/pytrik/sc_adipose/analyze_10x_fluidigm/data/10x')
```

#tSNE Plots

Below are several tSNE plots of the 10x data. tSNE was performed on the first 15 principal components of the log-normalized scaled (nUMI and percent.mito regressed out) data.

Visceral and perirenal seem a bit mixed, and supraclavicular and subcutaneous too. 

```{r}
TSNEPlot(all10x, pt.size=0.1, group.by='sample_name', do.label=T)
```

tSNE plots of samples within their subtissue.
Peri2 and Peri3 seem to overlap really well, as well as Supra1 and Supra2, and Visce1 and Visce3.

```{r results='hide'}
subtissues <- all10x@meta.data$sample_name2
t1 <- TSNEPlot(all10x, cells.use=all10x@cell.names[which(subtissues %in% 'Peri')], group.by='sample_name', pt.size=0.2)$plot
t2 <- TSNEPlot(all10x, cells.use=all10x@cell.names[which(subtissues %in% 'Subq')], group.by='sample_name', pt.size=0.2)$plot
t3 <- TSNEPlot(all10x, cells.use=all10x@cell.names[which(subtissues %in% 'Supra')], group.by='sample_name', pt.size=0.2)$plot
t4 <- TSNEPlot(all10x, cells.use=all10x@cell.names[which(subtissues %in% 'Visce')], group.by='sample_name', pt.size=0.2)$plot
```


```{r}
#plot_grid(t1, t2, t3, t4)
```


tSNE colored on subtissue.

```{r}
TSNEPlot(all10x, group.by='sample_name2', pt.size=0.1)
```

tSNE colored by cell cycle phase. 

```{r}
TSNEPlot(all10x, group.by='Phase', pt.size=0.1)
```

Some clustering with different resolutions.
res=0.5

```{r}
TSNEPlot(all10x, pt.size=0.1, group.by='res.0.5', do.label=T)
```

res=0.6

```{r}
TSNEPlot(all10x, pt.size=0.1, group.by='res.0.6')
```

res=0.7

```{r}
TSNEPlot(all10x, pt.size=0.1, group.by='res.0.7', do.label=T)
```

res=0.8

```{r}
TSNEPlot(all10x, pt.size=0.1, group.by='res.0.8', do.label=T)
```

res=0.9

```{r}
TSNEPlot(all10x, pt.size=0.1, group.by='res.0.9', do.label=T)
```

res=1

```{r}
TSNEPlot(all10x, pt.size=0.1, group.by='res.1', do.label=T)
```

#Cell cycle regression

```{r}
all10x.ccregout <- readRDS('/projects/pytrik/sc_adipose/analyze_10x_fluidigm/data/10x-ccregout')
```

tSNE of the cell cycle regressed out. There does not seem to be a lot of structure within samples now. 

```{r}
TSNEPlot(all10x.ccregout, pt.size=0.1, group.by='sample_name')
```


```{r}
TSNEPlot(all10x.ccregout, pt.size=0.1, group.by='Phase')
```

Subtissues

```{r}
subtissues <- all10x.ccregout@meta.data$sample_name2
t1 <- TSNEPlot(all10x.ccregout, cells.use=all10x.ccregout@cell.names[which(subtissues %in% 'Peri')], group.by='sample_name', pt.size=0.2)$plot
t2 <- TSNEPlot(all10x.ccregout, cells.use=all10x.ccregout@cell.names[which(subtissues %in% 'Subq')], group.by='sample_name', pt.size=0.2)$plot
t3 <- TSNEPlot(all10x.ccregout, cells.use=all10x.ccregout@cell.names[which(subtissues %in% 'Supra')], group.by='sample_name', pt.size=0.2)$plot
t4 <- TSNEPlot(all10x.ccregout, cells.use=all10x.ccregout@cell.names[which(subtissues %in% 'Visce')], group.by='sample_name', pt.size=0.2)$plot
#plot_grid(t1, t2, t3, t4)
```


#PCA

Some PCA plots. PC1 seems to capture cell cycle effects, and PC2 seems to capture some of the sample variability. 

```{r}
PCAPlot(all10x, group.by='Phase', pt.size=0.1)
```

```{r}
PCAPlot(all10x, group.by='sample_name', pt.size=0.1)
```

PCA plot of the cell cycle regressed out data. There is no cell cycle effect anymore. 

```{r}
PCAPlot(all10x.ccregout, group.by='Phase', pt.size=0.1)
```

```{r}
PCAPlot(all10x.ccregout, group.by='sample_name', pt.size=0.1)
```

#Alignment

Alignment of the data with and without cell cycle effects regressed out. Both were aligned on 30 subspaces, tSNE was performed on the first 15 CCs. 

```{r}
data.aligned <- readRDS('/projects/pytrik/sc_adipose/analyze_10x_fluidigm/data/10x-aligned')
data.aligned.ccregout <- readRDS('/projects/pytrik/sc_adipose/analyze_10x_fluidigm/data/10x-ccregout-aligned')
```

tSNE of the aligned data.

```{r}
TSNEPlot(data.aligned, group.by='sample_name', pt.size=0.1)
```

tSNE of the aligned data coloured on cell cycle phase.

```{r}
TSNEPlot(data.aligned, group.by='Phase', pt.size=0.1)
```


tSNE of the aligned data with cell cycle effects regressed out.

```{r}
TSNEPlot(data.aligned.ccregout, group.by='sample_name', pt.size=0.1)
```

tSNE of the aligned data with cell cycle effects regressed out, colored by phase.

```{r}
TSNEPlot(data.aligned.ccregout, group.by='Phase', pt.size=0.1)
```

tSNE of the aligned data with cell cycle effects regressed out, colored by subtissue

```{r}
TSNEPlot(data.aligned.ccregout, group.by='sample_name2', pt.size=0.1)
```


#Marker gene expression


```{r}

```


#Metadata


```{r}
FeaturePlot(all10x, c("nGene"), cols.use = c("grey","blue"), no.legend=F)
```

```{r}
FeaturePlot(all10x, c("percent.mito"), cols.use = c("grey","blue"), no.legend=F)
```


```{r}
FeaturePlot(all10x, c("nUMI"), cols.use = c("grey","blue"), no.legend=F)
```

Diff

```{r}
TSNEPlot(all10x, group.by='diff', pt.size=0.1)
```

ucp1.ctrl

```{r}
TSNEPlot(all10x, group.by='ucp1.ctrl', pt.size=0.1)
```

ucp1.ne

```{r}
TSNEPlot(all10x, group.by='ucp1.ne', pt.size=0.1)
```

bmi

```{r}
TSNEPlot(all10x, group.by='bmi', pt.size=0.1)
```

age 

```{r}
TSNEPlot(all10x, group.by='age', pt.size=0.1)
```


```{r}
VlnPlot(all10x, group.by='sample_name', features.plot=c('nGene'), point.size.use = -1, x.lab.rot=T)
```

```{r}
VlnPlot(all10x, group.by='sample_name', features.plot=c('nUMI'), point.size.use = -1, x.lab.rot=T)
```

```{r}
VlnPlot(all10x, group.by='sample_name', features.plot=c('percent.mito'), point.size.use = -1, x.lab.rot=T)
```

