---
title: "R Notebook"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: 
      smooth_scroll: true
---



```{r}
library(VennDiagram)
library(Seurat)
```


```{r}
markers <- read.table('../data/markergenes/markergenes-crossed', header=T)
```

Marker genes of the intersection of Supra and Peri. Supra has 99 marker genes, Peri 71. They have 9 genes in common.

```{r}
genes.peri <- markers[markers$cluster == 'Peri.white', 'gene']
genes.supra <- markers[markers$cluster == 'Supra.white', 'gene']
peri.supra <- intersect(genes.peri, genes.supra)

grid.newpage()
draw.pairwise.venn(length(genes.peri), length(genes.supra), length(peri.supra), category=c('Peri', 'Supra'), lty=rep('blank', 2), fill=c('#f67770', '#1fbfc3'), scaled=T, cat.fontfamily = rep("helvetica", 2))
```

Marker genes of the intersection of Subq and Visce. Subq has 65 marker genes, Visce 22. They have only 2 genes in common.

```{r}
genes.visce <- markers[markers$cluster == 'Visce.brown', 'gene']
genes.subq <- markers[markers$cluster == 'Subq.brown', 'gene']
visce.subq <- intersect(genes.visce, genes.subq)

grid.newpage()
draw.pairwise.venn(length(genes.visce), length(genes.subq), length(visce.subq), category=c('Visce', 'Subq'), lty=rep('blank', 2), fill=c('#c680fc', '#7dac1f'), scaled=T, cat.fontfamily = rep("helvetica", 2))
```

```{r}
all10x <- readRDS('../data/10x')
```

#Markers intersection Peri and Supra

```{r}
print(peri.supra)
```

```{r}
markers[which(markers$gene %in% peri.supra),]
```


```{r fig1, fig.height = 15, fig.width = 10, fig.align = "center"}
VlnPlot(all10x, features.plot=toupper(c('TM4SF1', 'MTRNR2L8', 'LY6K', 'MGST3', 'FHL2', 'COL6A2', 'TAGLN', 'HSPA8', 'PENK')), group.by='sample_name', point.size.use=-1, nCol=2, x.lab.rot=T, size.x.use=10)
```

#Markers intersection Subq and Visce

```{r}
print(visce.subq)
```

```{r}
print(markers[which(markers$gene %in% visce.subq),])
```


```{r fig2, fig.height = 3, fig.width = 10, fig.align = "center"}
VlnPlot(all10x, features.plot=toupper(c('GREM1', 'HOXB7')), group.by='sample_name', point.size.use=-1, nCol=2, x.lab.rot=T, size.x.use=10)
```

#Top markers Peri 

```{r}
print(markers[markers$cluster == 'Peri.white',][1:10,])
```


```{r fig3, fig.height = 15, fig.width = 10, fig.align = "center"}
VlnPlot(all10x, features.plot=as.vector(markers[markers$cluster == 'Peri.white',][1:10,'gene']), group.by='sample_name', point.size.use=-1, nCol=2, x.lab.rot=T, size.x.use=10)
```


#Top markers Supra

```{r}
print(markers[markers$cluster == 'Supra.white',][1:10,])
```

```{r fig4, fig.height = 15, fig.width = 10, fig.align = "center"}
VlnPlot(all10x, features.plot=as.vector(markers[markers$cluster == 'Supra.white',][1:10,'gene']), group.by='sample_name', point.size.use=-1, nCol=2, x.lab.rot=T, size.x.use=10)
```

#Top markers Visce

```{r}
print(markers[markers$cluster == 'Visce.brown',][1:10,])
```

Interestingly, some genes seem to be found because Supra4 and Subq4 are different. 

```{r fig5, fig.height = 15, fig.width = 10, fig.align = "center"}
VlnPlot(all10x, features.plot=as.vector(markers[markers$cluster == 'Visce.brown',][1:10,'gene']), group.by='sample_name', point.size.use=-1, nCol=2, x.lab.rot=T, size.x.use=10)
```

#Top markers Subq

```{r}
print(markers[markers$cluster == 'Subq.brown',][1:10,])
```

Most of the markers for Subq seem to be found because Subq_3 stands out (RPS29, BCYRN1, RPL36A, ATP5I, AC009501.4, RPS10). Mostly ribosomal genes.

BCYRN1 = brain cytoplasmic RNA

```{r fig6, fig.height = 15, fig.width = 10, fig.align = "center"}
VlnPlot(all10x, features.plot=as.vector(markers[markers$cluster == 'Subq.brown',][1:10,'gene']), group.by='sample_name', point.size.use=-1, nCol=2, x.lab.rot=T, size.x.use=10)
```

