---
title: "R Notebook"
output: html_notebook
---

Setup:
1. Trajectories
2. Trajectories cell cycle regressed out
3. Trajectories cell cycle + nUMI + percent.mito regressed out
4. Trajectories nUMI + percent.mito regressed out


```{r}
.libPaths('/home/cbmr/pytrik/libraries/')
setwd('/projects/pytrik/sc_adipose/analyze_10x_fluidigm/notebooks/')
library(monocle)
library(Seurat)
```

Analyzing trajectories per depot (cc effect, nUmi and percent.mito not regressed out here).

```{r}
peri <- readRDS('../data/monocle/10x_monocle_Peri')
visce <- readRDS('../data/monocle/10x_monocle_Visce')
subq <- readRDS('../data/monocle/10x_monocle_Subq')
supra <- readRDS('../data/monocle/10x_monocle_Supra')

pData(peri)['samplename'] <- pData(peri)['sample_name']
pData(visce)['samplename'] <- pData(visce)['sample_name']
pData(subq)['samplename'] <- pData(subq)['sample_name']
pData(supra)['samplename'] <- pData(supra)['sample_name']

```

##1. Cell trajectories
Cell trajectories per depot, colored on sample. 

```{r}
plot_grid(plot_cell_trajectory(peri, color_by='samplename', cell_size=0.5),
          plot_cell_trajectory(visce, color_by='samplename', cell_size=0.5),
          plot_cell_trajectory(subq, color_by='samplename', cell_size=0.5),
          plot_cell_trajectory(supra, color_by='samplename', cell_size=0.5),
          labels = c('Peri', 'Visce', 'Subq', 'Supra'))
```

And colored on cell cycle state. 

```{r}
plot_grid(plot_cell_trajectory(peri, color_by='Phase', cell_size=0.5),
          plot_cell_trajectory(visce, color_by='Phase', cell_size=0.5),
          plot_cell_trajectory(subq, color_by='Phase', cell_size=0.5),
          plot_cell_trajectory(supra, color_by='Phase', cell_size=0.5),
          labels = c('Peri', 'Visce', 'Subq', 'Supra'))
```

##2. Trajectories with nUMI and percent.mito regressed out

Look at the cell trajectories of the depots with nUMI and percent.mito regressed out. 

```{r}
peri.numi.pm <- readRDS('../data/monocle/10x_monocle_Peri_pm-umi')
visce.numi.pm <- readRDS('../data/monocle/10x_monocle_Visce_pm-umi')
subq.numi.pm <- readRDS('../data/monocle/10x_monocle_Subq_pm-umi')
supra.numi.pm <- readRDS('../data/monocle/10x_monocle_Supra_pm-umi')

pData(peri.numi.pm)['samplename'] <- pData(peri.numi.pm)['sample_name']
pData(visce.numi.pm)['samplename'] <- pData(visce.numi.pm)['sample_name']
pData(subq.numi.pm)['samplename'] <- pData(subq.numi.pm)['sample_name']
pData(supra.numi.pm)['samplename'] <- pData(supra.numi.pm)['sample_name']
```

Cell trajectories colored on sample.

```{r}
plot_grid(plot_cell_trajectory(peri.numi.pm, color_by='samplename', cell_size=0.5),
          plot_cell_trajectory(visce.numi.pm, color_by='samplename', cell_size=0.5),
          plot_cell_trajectory(subq.numi.pm, color_by='samplename', cell_size=0.5),
          plot_cell_trajectory(supra.numi.pm, color_by='samplename', cell_size=0.5),
          labels = c('Peri', 'Visce', 'Subq', 'Supra'))
```

```{r}
plot_grid(plot_cell_trajectory(peri.numi.pm, color_by='Phase', cell_size=0.5),
          plot_cell_trajectory(visce.numi.pm, color_by='Phase', cell_size=0.5),
          plot_cell_trajectory(subq.numi.pm, color_by='Phase', cell_size=0.5),
          plot_cell_trajectory(supra.numi.pm, color_by='Phase', cell_size=0.5),
          labels = c('Peri', 'Visce', 'Subq', 'Supra'))
```

##3. Trajectories with cell cycle regressed out

```{r}
#setwd('/projects/pytrik/sc_adipose/analyze_10x_fluidigm/')
peri.cc <- readRDS('../data/monocle/10x_monocle_Peri-cc')
visce.cc <- readRDS('../data/monocle/10x_monocle_Visce-cc')
subq.cc <- readRDS('../data/monocle/10x_monocle_Subq-cc')
supra.cc <- readRDS('../data/monocle/10x_monocle_Supra-cc')

pData(peri.cc)['samplename'] <- pData(peri.cc)['sample_name']
pData(visce.cc)['samplename'] <- pData(visce.cc)['sample_name']
pData(subq.cc)['samplename'] <- pData(subq.cc)['sample_name']
pData(supra.cc)['samplename'] <- pData(supra.cc)['sample_name']
```


```{r}
plot_grid(plot_cell_trajectory(peri.cc, color_by='samplename', cell_size=0.5),
          plot_cell_trajectory(visce.cc, color_by='samplename', cell_size=0.5),
          plot_cell_trajectory(subq.cc, color_by='samplename', cell_size=0.5),
          plot_cell_trajectory(supra.cc, color_by='samplename', cell_size=0.5),
          labels = c('Peri', 'Visce', 'Subq', 'Supra'))
```

```{r}
plot_grid(plot_cell_trajectory(peri.cc, color_by='Phase', cell_size=0.5),
          plot_cell_trajectory(visce.cc, color_by='Phase', cell_size=0.5),
          plot_cell_trajectory(subq.cc, color_by='Phase', cell_size=0.5),
          plot_cell_trajectory(supra.cc, color_by='Phase', cell_size=0.5),
          labels = c('Peri', 'Visce', 'Subq', 'Supra'))
```


##4. Trajectories with cell cycle, percent.mito and nUMI regressed out

```{r}
peri.ccout3 <- readRDS('../data/monocle/10x_monocle_Peri_pm-umi-cc')
visce.ccout3 <- readRDS('../data/monocle/10x_monocle_Visce_pm-umi-cc')
subq.ccout3 <- readRDS('../data/monocle/10x_monocle_Subq_pm-umi-cc')
supra.ccout3 <- readRDS('../data/monocle/10x_monocle_Supra_pm-umi-cc')

pData(peri.ccout3)['samplename'] <- pData(peri.ccout3)['sample_name']
pData(visce.ccout3)['samplename'] <- pData(visce.ccout3)['sample_name']
pData(subq.ccout3)['samplename'] <- pData(subq.ccout3)['sample_name']
pData(supra.ccout3)['samplename'] <- pData(supra.ccout3)['sample_name']

plot_grid(plot_cell_trajectory(peri.ccout3, color_by='samplename', cell_size=0.5),
          plot_cell_trajectory(visce.ccout3, color_by='samplename', cell_size=0.5),
          plot_cell_trajectory(subq.ccout3, color_by='samplename', cell_size=0.5),
          plot_cell_trajectory(supra.ccout3, color_by='samplename', cell_size=0.5),
          labels = c('Peri', 'Visce', 'Subq', 'Supra'))
```



```{r}
plot_grid(plot_cell_trajectory(peri.ccout3, color_by='Phase', cell_size=0.5),
          plot_cell_trajectory(visce.ccout3, color_by='Phase', cell_size=0.5),
          plot_cell_trajectory(subq.ccout3, color_by='Phase', cell_size=0.5),
          plot_cell_trajectory(supra.ccout3, color_by='Phase', cell_size=0.5),
          labels = c('Peri', 'Visce', 'Subq', 'Supra'))
```


