---
title: "R Notebook"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: 
      smooth_scroll: true
---

```{r}
library(Seurat)
library(scmap)
library(SingleCellExperiment)
library(dplyr)
```


Data loading and inspection of the metadata.

```{r}
seurat_obj <- readRDS('/projects/pytrik/sc_adipose/analyze_10x_fluidigm/data/downloads/MACA_data_PCA_clustering')
head(seurat_obj@meta.data)
```

```{r}
sce_maca <- as.SingleCellExperiment(seurat_obj)
all10x <- readRDS('/projects/pytrik/sc_adipose/analyze_10x_fluidigm/data/10x-180504')
sce_10x <- as.SingleCellExperiment(all10x)

#convert maca gene names to uppercase to match 10x gene names
rowData(sce_maca)['feature_symbol'] <- unlist(lapply(rowData(sce_maca)$gene, function(x){return(toupper(x))}))
rowData(sce_10x)['feature_symbol'] <- rowData(sce_10x)$gene

counts(sce_10x) <- as.matrix(counts(sce_10x))
logcounts(sce_10x) <- as.matrix(logcounts(sce_10x))

counts(sce_maca) <- as.matrix(counts(sce_maca))
logcounts(sce_maca) <- as.matrix(logcounts(sce_maca))
sce_maca <- selectFeatures(sce_maca, suppress_plot = FALSE)
```

#Running scmap on the whole MACA dataset

Setting the right column for clustering.

```{r}
sce_maca <- indexCluster(sce_maca, cluster_col = 'res.40')
```

Predicting cell types in our dataset. Now we can use a higher threshold and still get a lot of assignments. 

```{r}
scmapCluster_results <- scmapCluster(
  projection = sce_10x, 
  index_list = list(
    sce_maca = metadata(sce_maca)$scmap_cluster_index
  ),
  threshold=0.7  #default=0.7 
)

predictions_all <- as.data.frame(table(scmapCluster_results$scmap_cluster_labs)) 
predictions_all <- predictions_all[order(-predictions_all$Freq),]
as.data.frame(predictions_all)
```

Var1 is the cluster number, Freq the amount of predictions in our dataset

Which cells are in cluster 289?

```{r}
as.data.frame(table(seurat_obj@meta.data$tissue_cell_type[seurat_obj@meta.data$res.40 == 289]))
```

And which cells are in 304?

```{r}
as.data.frame(table(seurat_obj@meta.data$tissue_cell_type[seurat_obj@meta.data$res.40 == 304]))
```


```{r}
predicted_labels <- as.data.frame(
    row.names=rownames(sce_10x@colData), 
    x=as.vector(scmapCluster_results$scmap_cluster_labs))
names(predicted_labels) <- 'predicted_labels'
all10x <- AddMetaData(all10x, metadata=predicted_labels, col.name='predicted_labels')
#TSNEPlot(all10x, group.by='predicted_labels', pt.size=0.1, do.label=T)

all10x@meta.data['predicted_labels_clean'] <- all10x@meta.data$predicted_labels
all10x@meta.data[which(all10x@meta.data$predicted_labels %in% predictions_all$Var1[4:length(predictions_all$Var1)]), 'predicted_labels_clean'] = 'unassigned' 

TSNEPlot(all10x, group.by='predicted_labels_clean', pt.size=0.1)
```

In the MACA data, cluster 289 mostly contains mammary basal cells (35) and mammary stromal cells (14). Cluster 304 mostly contains mammary stromal cells (35) and fat mesenchymal stem cells (10). 

Since cluster 289 only contains 59 cells, this also shows the homogeneity of our cells, because more than 40.000 of our cells are closest to only these 59 cells in the MACA dataset. 

```{r}
subset <- SubsetData(SetAllIdent(seurat_obj, id='res.40'), ident.use=c(289, 304))
subset <- RunPCA(subset, pcs.compute=50)
subset <- RunTSNE(subset, dims.use=1:15)
TSNEPlot(subset, group.by='res.40', pt.size=1)
```

```{r fig1, fig.height=4, fig.width=8, fig.align="center"}
TSNEPlot(subset, group.by='tissue_cell_type')
```

